Fractional Types

### 2013-02-23 frac.tex
removed type diagrams from section 4

\noindent At the type level, the computation proceeds as follows:
%subcode{bnf} include main
%  (b1 :-* b2) * b1 &=& (1/b1 * b2) * b1 & 
%     &<->& b1 * (1/b1 * b2) & (swap*)
%     &<->& (b1 * 1/b1) * b2) & (assocl*)
%     &<->& (1/b1 * b1) * b2) & (swap* (*) id)
%     &<->& 1 * b2 & (eps*_{b1} (*) id)
%     &<->& b2 & (unite)

@@

\noindent Again, at the type level, the computation proceeds as follows:

%subcode{bnf} include main
%  (b1 :-* b2) * (b2 :-* b3) &=& (1/b1 * b2) * (1/b2 * b3) & 
%     &<->& (1/b1 * (b2 * (1/b2 * b3)) & (assocr*)
%     &<->& (1/b1 * b3) & (id * apply')
%     &=& b1 :-* b3

@@

\noindent
where {{reorder}} is the obvious combinator of type {{b1 * (b2 * b3) * b4 <-> b1
* (b3 * b2) * b4}}. At the type level, the computation proceeds as follows:

%% XXX: why won't the columnstyle declaration here work? (Z)
%subcode{opsem} include main
%! columnStyle = rlr
%        & 1/(b1 * b2) & 
%     <->& 1 * 1/(b1 * b2) & (uniti)
%     <->& 1 * (1 * 1/(b1 * b2)) & (uniti)
%     <->& (1 * 1) * 1/(b1 * b2) & (assocl*)
%     <->& ((1/b1 * b1) * (1/b2 * b2)) * 1/(b1 * b2) &((eta*_{b1} (*) eta*_{b2}) (*) id)
%     <->& ((1/b1 * 1/b2) * (b1 * b2)) * 1/(b1 * b2) & (reoder (*) id)
%     <->& (1/b1 * 1/b2) * ((b1 * b2) * 1/(b1 * b2)) & (assocr*)
%     <->& (1/b1 * 1/b2) * (1/(b1 * b2) * (b1 * b2)) & (id * swap*)
%     <->& (1/b1 * 1/b2) * 1 & (id * eps*)
%     <->& 1 * (1/b1 * 1/b2) & (swap*)
%     <->& (1/b1 * 1/b2) & (unite)

\noindent
With {{recip}} out of the way, we can easily write {{curry}}:

@@

\noindent At the type level, this computation proceeds as follows:

%subcode{bnf} include main
%  b &<->& (1 * b) & (uniti)
%    &<->& (1/(1/b) * 1/b) * b & (eta*_{1/b} (*) id)
%    &<->& 1/(1/b) * (1/b * b) & (assocr*)
%    &<->& 1/(1/b) * 1 & (id (*) eps*_b)
%    &<->& 1 * 1/(1/b) & (swap*)
%    &<->& 1/(1/b) & (unite)

>>>>

@@

@@

\noindent
where {{reorder}} is the obvious combinator of type {{b1 * (b2 * b3) * b4 <-> b1 * (b3 * b2) * b4}}.
With {{recip}} out of the way, we can easily write {{curry}}:

@@
